---
title: "Battery Charge"
author: "Kevin Kent"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readr)
library(tidyverse)
options(digits = 4)
my_bat <- read_csv("Data/Battery.csv", col_names = FALSE, col_types = "inD")
names(my_bat) <- c("Battery", "Voltage", "Date")

by_bat <- my_bat %>% group_by(Battery)


t_by_bat <- by_bat %>% summarise("Min_V" = sprintf(min(Voltage), fmt = '%#.2f'), 
                     "Max_V" = sprintf(max(Voltage), fmt = '%#.2f'),
                     "Cycles" = n())



by_date <- my_bat %>% group_by(Date)

t_by_day <- by_date %>% summarise("Avg_V" = mean(Voltage), "Count" = n())
min_d <- min(my_bat$Date)
max_d <- max(my_bat$Date)
```

# Battery Charge

The battery type is LiPo with six cells ('6S') of nominal 3.7 volts each. The battery voltage is usually set to 4.2V for charging purposes for a total voltage of 25.2V. At each charge cycle the battery voltage is recorded. The following shows the battery charge log from `r min_d` to `r max_d`.  

## Charge Totals

The following table shows the minimum and maximum values for the voltage after each battery is charged. The 'Cycles' column shows the total number of times the battery has been charged. Batteries with number 21 and up are 7000mAh, the others are 5000mAh. 

```{r by_battery}
knitr::kable(t_by_bat)

```

\newpage
## Daily Charging

The following shows the number of batteries charged per day. Note that any individual battery may have been charged more than once per day.  


```{r by_day, echo=FALSE}
knitr::kable(t_by_day)
```


```{r hist, echo=FALSE}
library(ggplot2)
v <- ggplot(my_bat, aes(x=Voltage)) + 
  geom_histogram(color="black", fill="blue", binwidth = .01) + 
  ggtitle("Final Charge Voltage") + 
  labs(x = "Voltage", y = "Charge Counts")
v

```
